---
title: "AM PG with asymmetry"
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
---

# Settings

## Data import and clear environment

Import of the raw dataset "data.xlsx".

```{r}
rm(list = ls())
#dt = readxl::read_xlsx("C://data.xlsx")
```


## Packages

Packages used in this code.

```{r message=FALSE, warning=FALSE, include=FALSE}
library(stargazer)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(FactoMineR)
library(factoextra)
library(dunn.test)
library(sandwich)
library(lmtest)
library(Kendall)
library(pwr)
```


# Database reworks

## Exclusion

Data excluded from the analysis. The equal treatment is the replication from the original paper. The session mfzczcqd has been removed because one player left during the session but we finished the session to be able to pay the other players.

```{r}

DATAf <- dt %>% filter(!is.na(activite_A) & activite_A != "")
DATA <- DATAf %>% filter(treatment != "equal")
DATAeq <- DATAf %>% filter(treatment == "equal")
DATA <- DATA %>% filter(session != "mfzczcqd") #Session excluded because of the outlier

```

## New variables

Here, we construct additional variables derived from the original data.
These variables may include theoretical predictions, treatment indicators, or transformation of raw variables.

```{r}

# Inequality level variable
names(DATA)[names(DATA) == "treatment"] = "ineq_level"

# Treatment variable
names(DATA)[names(DATA) == "with_approbation"] = "trt"
DATA$trt[DATA$trt == "0"] = "baseline"
DATA$trt[DATA$trt == "1"] = "am"


# Treatment variable by inequality level
DATA$subtrt <- paste(DATA$ineq_level, DATA$trt, sep = "_")

DATA$subtrt[DATA$subtrt == "equal_baseline"] = "eq_no_am"
DATA$subtrt[DATA$subtrt == "equal_am"] = "eq_am"
DATA$subtrt[DATA$subtrt == "low_baseline"] = "low_no_am"
DATA$subtrt[DATA$subtrt == "low_am"] = "low_am"
DATA$subtrt[DATA$subtrt == "high_baseline"] = "high_no_am"
DATA$subtrt[DATA$subtrt == "high_am"] = "high_am"

# Final group contribution variable
DATA$final_group_contrib <- ifelse(DATA$trt == "am", 
                                    DATA$group_total_activite_A_apres_approb, 
                                    DATA$group_total_activite_A)

# Role variable
DATA <- DATA %>%
  mutate(role = case_when(
    dotation %in% c(22, 30) ~ "rich",
    dotation %in% c(10, 18) ~ "poor",
    dotation == 20 ~ "equal",
    TRUE ~ NA_character_ 
  ))

# Other's dotation variable
names(DATA)[names(DATA) == "dotation"] = "w_i"
DATA <- DATA %>%
  mutate(w_j = case_when(
    w_i == 20 ~ 20,
    w_i == 22 ~ 18,
    w_i == 30 ~ 10,
    w_i == 10 ~ 30,
    w_i == 18 ~ 22,
    TRUE ~ w_i 
  ))

# Other's contribution variable
DATA$g_i = ifelse(DATA$trt == "am", 
                  DATA$activite_A_apres_approb, 
                  DATA$activite_A)
DATA$g_j = ifelse(DATA$trt == "am", 
                  DATA$group_total_activite_A_apres_approb-DATA$activite_A_apres_approb, 
                  DATA$group_total_activite_A-DATA$activite_A)

# Other's profit variable
names(DATA)[names(DATA) == "payoff_ecus"] = "pi_i"
DATA$pi_j = DATA$w_j - DATA$g_j + 0.7 * (DATA$g_i + DATA$g_j)

# Group wealth
DATA$w_g = 40

# Absolute inequality variation variable
DATA <- DATA %>%
  mutate(var_AI = case_when(
    role == "poor" ~ (pi_j - pi_i) - (w_j - w_i),
    role == "rich" ~ (pi_i - pi_j) - (w_i - w_j),
    role == "equal" ~ abs(pi_i - pi_j),
    TRUE ~ NA_real_
  ))

DATA <- DATA %>%
  mutate(var_RI = case_when(
    role == "poor" ~ (pi_i / (pi_i + pi_j)) - (w_i / (w_i + w_j)),
    role == "rich" ~ (pi_j / (pi_i + pi_j)) - (w_j / (w_i + w_j)),
    role == "equal" ~ abs((pi_i / (pi_i + pi_j)) - (1/2)),
    TRUE ~ NA_real_ 
  ))


partner_activite_A <- DATA %>%
  select(participant, round_number, group, activite_A) %>%
  rename(partner = participant, activite_A_partner = activite_A)

DATA <- DATA %>%
  left_join(partner_activite_A, by = c("round_number", "group")) %>%
  filter(participant != partner) %>%
  select(-partner)

DATA <- DATA %>%
  relocate(activite_A_partner, .after = activite_A)

```

# Theoretical predictions

This section generates variables based on the theoretical model's predictions.

```{r}

# Nash equilibrium for selfish agents
DATA <- DATA %>%
  mutate(
    nash_eq = case_when(
      trt == "am" & role == "rich" ~ w_g - w_i,
      trt == "am" & role == "poor" ~ w_i,
      trt == "am" & role == "equal" ~ w_i,
      trt == "baseline" ~ 0,
      TRUE ~ NA_real_
    )
  )
DATA$nash_eq_g = 2 * DATA$nash_eq


# Efficient equilibrium
DATA$efficient_eq = DATA$w_i
DATA$efficient_eq_g = DATA$w_g
```


# Summary

Provides summary statistics of the main variables across groups or treatments.

```{r}
# Number of observations
table(DATA$trt)
table(DATA$subtrt)
table(DATA$ineq_level)
table(DATA$role)
```

## Individual characteristics

```{r}

# Age, Gender, Brotherhood
descriptive_stats <- DATA %>%
  group_by(subtrt) %>%
  summarise(
    mean_g_i = mean(g_i, na.rm = TRUE),
    mean_age = mean(age, na.rm = TRUE),
    median_age = median(age, na.rm = TRUE),
    percent_female = sum(gender == "Féminin") / n() * 100,
    mean_brotherhood = mean(brotherhood, na.rm = TRUE),
    mean_brotherh_rank = mean(brotherhood_rank, na.rm = TRUE),
    understanding_faults = mean(understanding_faults)
  )
print(descriptive_stats)

# Nationality
unique_participants <- DATA %>%
  distinct(participant, .keep_all = TRUE)
nationality_counts <- unique_participants %>%
  count(nationality, sort = TRUE)
print(nationality_counts)

# Marital status
marital_counts <- unique_participants %>%
  count(marital_status, sort = TRUE)
print(marital_counts)

# Job
job_counts <- unique_participants %>%
  count(job, sort = TRUE)
print(job_counts)

# Sociopro Group
socio_counts <- unique_participants %>%
  count(socioprofessional_group, sort = TRUE)
print(socio_counts)

# Sociopro Group
socio_counts <- unique_participants %>%
  count(socioprofessional_group, sort = TRUE)
print(socio_counts)

# Financial health
fi_abs_counts <- unique_participants %>%
  count(sante_financiere_abs, sort = TRUE)
print(fi_abs_counts)
fi_stat_counts <- unique_participants %>%
  count(sante_financiere_rel_status, sort = TRUE)
print(fi_stat_counts)
fi_fr_counts <- unique_participants %>%
  count(sante_financiere_rel_france, sort = TRUE)
print(fi_fr_counts)
fi_wrld_counts <- unique_participants %>%
  count(sante_financiere_rel_monde, sort = TRUE)
print(fi_wrld_counts)

# Understanding faults
under_faults_counts <- unique_participants %>%
  count(understanding_faults, sort = TRUE)
print(under_faults_counts)

```

## Decision summary statistics

```{r}

mean_gi_ineq_trt <- DATA %>%
  group_by(ineq_level, trt) %>%
  summarise(mean_gi = mean(g_i, na.rm = TRUE)) %>%
  ungroup()

# Calculate mean g_i by role, ineq_level, and trt
mean_gi_role_ineq_trt <- DATA %>%
  group_by(role, ineq_level, trt) %>%
  summarise(mean_gi = mean(g_i, na.rm = TRUE)) %>%
  ungroup()

# Print the tables
print(mean_gi_ineq_trt)
print(mean_gi_role_ineq_trt)


# In the replication
mean_gi_trt <- dt %>%
  group_by(treatment, with_approbation) %>%
  summarise(mean_gi = mean(activite_A_apres_approb, na.rm = TRUE)) %>%
  ungroup()

print(mean_gi_trt)

mean_gi_trt <- dt %>%
  filter(dt$round_number >9) %>%
  group_by(treatment, with_approbation) %>%
  summarise(mean_gi = mean(activite_A_apres_approb, na.rm = TRUE)) %>%
  ungroup()

print(mean_gi_trt)

# In the replication
mean_prop_trt <- dt %>%
  group_by(treatment, with_approbation) %>%
  summarise(mean_prop = mean(activite_A, na.rm = TRUE)) %>%
  ungroup()

print(mean_prop_trt)

mean_prop_trt <- dt %>%
  filter(dt$round_number >9) %>%
  group_by(treatment, with_approbation) %>%
  summarise(mean_prop = mean(activite_A, na.rm = TRUE)) %>%
  ungroup()

print(mean_prop_trt)

mean_prop_trt <- DATA %>%
  group_by(trt, ineq_level, role) %>%
  summarise(mean_prop = mean(activite_A, na.rm = TRUE)) %>%
  ungroup()

print(mean_prop_trt)



```


# Estimation of parameters

Estimation of the alpha and beta parameters of Fehr and Schmidt 1999 based on the method of Blanco et al. 2011.

```{r}

## Equality threshold dictator game (ETDG)
hist(DATA$ETDG_switch)
## Modified Ultimatum game (MUG)
hist(DATA$MUG_decideur_option)
hist(DATA$MUG_receveur_option)
## Modified Dictator game (MDG)
hist(DATA$MDG_option)

ggplot(DATA, aes(x = ETDG_switch)) +
  geom_histogram(aes(y = ..count../sum(..count..) * 100), bins = 30) +
  labs(title = "Percentage of Participants by ETDG Switch",
       x = "ETDG Switch",
       y = "Percentage (%)") +
  theme_minimal()

ggplot(DATA, aes(x = MUG_decideur_option)) +
  geom_histogram(aes(y = ..count../sum(..count..) * 100), bins = 30) +
  labs(title = "Percentage of Participants by MUG Decider Option",
       x = "MUG Decider Option",
       y = "Percentage (%)") +
  theme_minimal()

ggplot(DATA, aes(x = MUG_receveur_option)) +
  geom_histogram(aes(y = ..count../sum(..count..) * 100), bins = 30, fill = "skyblue", color = "black") +
  geom_text(stat = "bin", 
            aes(y = ..count../sum(..count..) * 100, 
                label = paste0(round(..count../sum(..count..) * 100, 1), "%")), 
            bins = 30, 
            vjust = -0.5, 
            size = 3) +
  labs(title = "Percentage of Participants by MUG Receiver Option",
       x = "MUG Receiver Option",
       y = "Percentage (%)") +
  theme_minimal()

DATA$beta = 1 - ((DATA$ETDG_switch-0.5-1) / 20) # -0.5 for approximation (Blanco et al. 2011) and -1 because the variable is coded from 1 to 21
DATA$alpha = ((DATA$MUG_receveur_option-0.5)) / (2*(10-(DATA$MUG_receveur_option-0.5))) # -0.5 for approximation (Blanco et al. 2011)

beta_plot <- ggplot(DATA, aes(x = beta)) +
  geom_bar() +
  labs(title = "Frequency of Participants by Beta values (Fehr & Scmidt advantageous inequalities)",
       x = "Beta",
       y = "Frequency") +
  theme_minimal()

alpha_plot <- ggplot(DATA, aes(x = alpha)) +
  geom_bar() +
  labs(title = "Frequency of Participants by Alpha values (Fehr & Scmidt disadvantageous inequalities)",
       x = "Alpha",
       y = "Frequency") +
  theme_minimal()

print(beta_plot)
print(alpha_plot)
```

## Figure 4.......................!!!

```{r}
DATA$alpha_display <- ifelse(DATA$alpha > 4.5, 4.5, DATA$alpha)
DATA$alpha_label <- ifelse(DATA$alpha > 4.5, ">4.5", "")

ggplot(DATA, aes(x = alpha_display, y = beta)) +
  geom_point() +  
  geom_abline(slope = 1, intercept = 0, lty = 5, color = "coral3", size = 1.2) + 
  geom_hline(yintercept = 1, lty = 2, color = "blue", size = 1.2)
  labs(title = expression("Scatter Plot of " * alpha ~ "vs." ~ beta ~ "with" ~ beta == alpha ~ "Line"),
       x = expression(alpha),
       y = expression(beta)) +
  theme_minimal() +
  scale_x_continuous(breaks = c(seq(0, 4, by = 0.5), 4.5), labels = c(seq(0, 4, by = 0.5), ">4.5"))

```

```{r}
DATA$alpha_display <- ifelse(DATA$alpha > 4.5, 4.5, DATA$alpha)
DATA$alpha_label <- ifelse(DATA$alpha > 4.5, ">4.5", "")

participant_counts <- DATA %>%
  group_by(alpha_display, beta) %>%
  summarise(unique_participants = n_distinct(participant), .groups = 'drop') 

DATA <- merge(DATA, participant_counts, by = c("alpha_display", "beta"), all.x = TRUE)

ggplot(DATA, aes(x = alpha_display, y = beta, size = unique_participants)) +
  geom_point(alpha = 0.6) +  
  geom_abline(slope = 1, intercept = 0, lty = 5, color = "coral3", size = 1.2) +  
  geom_hline(yintercept = 1, lty = 2, color = "blue", size = 1.2) +
  labs(title = expression("Scatter Plot of " * alpha ~ "vs." ~ beta ~ "with" ~ beta == alpha ~ "Line"),
       x = expression(alpha),
       y = expression(beta),
       size = "Unique\nParticipants") + 
  theme_minimal() +
  scale_x_continuous(breaks = c(seq(0, 4, by = 0.5), 4.5), labels = c(seq(0, 4, by = 0.5), ">4.5")) + 
  guides(size = guide_legend(override.aes = list(alpha = 1)))
```


## Append A.3..................!!!

```{r}
DATA$alpha_interval <- cut(DATA$alpha,
                           breaks = c(-Inf, 0.4, 0.92, 4.5, Inf),
                           labels = c("< 0.4", ">= 0.4 and < 0.92", ">= 0.92 and < 4.5", ">= 4.5"),
                           right = FALSE)

alpha_percentages <- DATA %>%
group_by(alpha_interval) %>%
summarise(Count = n(),
Percentage = (n() / nrow(DATA)) * 100) %>%
ungroup() #

DATA$beta_interval <- cut(DATA$beta,
                          breaks = c(-Inf, 0.235, 0.5, Inf),
                          labels = c("< 0.235", ">= 0.235 and < 0.5", ">= 0.5"),
                          right = FALSE)

beta_percentages <- DATA %>%
group_by(beta_interval) %>%
summarise(Count = n(),
Percentage = (n() / nrow(DATA)) * 100) %>%
ungroup()

print(alpha_percentages)
print(beta_percentages)

data <- data.frame(
  Interval = c("alpha < 0.4", "0.4 <= alpha < 0.92", "0.92 <= alpha < 4.5", "4.5 <= alpha",
               "beta < 0.235", "0.235 <= beta < 0.5", "0.5 <= beta"),
  F_S = c(30, 30, 30, 10, 30, 30, 40),
  Blanco_et_al = c(31, 33, 23, 13, 29, 15, 56),
  Our_Data = c(21, 20, 29, 31, 21, 28, 51)
)

alpha_data <- data[1:4, ]
beta_data <- data[5:7, ]

chisq_test_alpha <- chisq.test(rbind(alpha_data$F_S, alpha_data$Blanco_et_al, alpha_data$Our_Data))
print("Chi-square test for Alpha Distribution:")
print(chisq_test_alpha)

chisq_test_beta <- chisq.test(rbind(beta_data$F_S, beta_data$Blanco_et_al, beta_data$Our_Data))
print("Chi-square test for Beta Distribution:")
print(chisq_test_beta)

chisq_test_alpha_blanco <- chisq.test(rbind(alpha_data$Our_Data, alpha_data$Blanco_et_al))
print("Chi-square test for Alpha Distribution (Our Data vs Blanco et al.):")
print(chisq_test_alpha_blanco)

chisq_test_alpha_fs <- chisq.test(rbind(alpha_data$Our_Data, alpha_data$F_S))
print("Chi-square test for Alpha Distribution (Our Data vs F&S):")
print(chisq_test_alpha_fs)

chisq_test_beta_blanco <- chisq.test(rbind(beta_data$Our_Data, beta_data$Blanco_et_al))
print("Chi-square test for Beta Distribution (Our Data vs Blanco et al.):")
print(chisq_test_beta_blanco)

chisq_test_beta_fs <- chisq.test(rbind(beta_data$Our_Data, beta_data$F_S))
print("Chi-square test for Beta Distribution (Our Data vs F&S):")
print(chisq_test_beta_fs)

```

# Theory testing

## Prop 1: Lowest contributor always approves

```{r}
DATA_am <- filter(DATA, DATA$trt=="am")

DATA_am$prop1 <- ifelse(DATA_am$activite_A < DATA_am$activite_A_partner, 1, 0)
DATA_am$irrational_not_approving <- ifelse(DATA_am$prop1 == 1 & DATA_am$approbation == 0, 1, 0)

DATA_am_prop1 <- filter(DATA_am, prop1 == 1)

count_approbation_1 <- sum(DATA_am_prop1$approbation == 1)

percentage <- (count_approbation_1 / nrow(DATA_am_prop1)) * 100

print(paste("Percentage of players with prop1 == 1 and approbation == 1: ", percentage, "%"))

```


## Prop 2: Highest contributor always disapproves

```{r}
DATA_am$prop2 <- ifelse(DATA_am$activite_A > DATA_am$activite_A_partner,1,0)
DATA_am$irrational_not_disapproving <- ifelse(DATA_am$prop2 == 1 & DATA_am$approbation == 1, 1, 0)

DATA_am_prop2 <- filter(DATA_am, prop2 == 1)

count_approbation_2 <- sum(DATA_am_prop2$approbation == 0)

percentage <- (count_approbation_2 / nrow(DATA_am_prop2)) * 100

print(paste("Percentage of players with prop2 == 1 and approbation == 0: ", percentage, "%"))
```

### Who propose the most?

```{r}
DATA_am$prop_less <- ifelse(DATA_am$activite_A < DATA_am$activite_A_partner,1,0)
DATA_am$prop_more <- ifelse(DATA_am$activite_A > DATA_am$activite_A_partner,1,0)
DATA_am$prop_equal <- ifelse(DATA_am$activite_A == DATA_am$activite_A_partner,1,0)

count_rich1 <- DATA_am %>%
  filter(role == "rich", prop_less == 1) %>%
  nrow()

count_poor1 <- DATA_am %>%
  filter(role == "poor", prop_less == 1) %>%
  nrow()

count_rich2 <- DATA_am %>%
  filter(role == "rich", prop_more == 1) %>%
  nrow()

count_poor2 <- DATA_am %>%
  filter(role == "poor", prop_more == 1) %>%
  nrow()

count_rich3 <- DATA_am %>%
  filter(role == "rich", prop_equal == 1) %>%
  nrow()

count_poor3 <- DATA_am %>%
  filter(role == "poor", prop_equal == 1) %>%
  nrow()

print(paste("Count for rich and prop_equal == 1:", count_rich3))
print(paste("Count for poor and prop_equal == 1:", count_poor3))
print(paste("Count for rich and prop_more == 1:", count_rich2))
print(paste("Count for poor and prop_more == 1:", count_poor2))
print(paste("Count for rich and prop_less == 1:", count_rich1))
print(paste("Count for poor and prop_less == 1:", count_poor1))
```


### Figure 5.....................!!!

```{r}
DATA_irrat_dis <- DATA_am %>%
  group_by(participant) %>%
  summarise(
    irrational_not_disapproving = sum(irrational_not_disapproving),
    role = first(role),
    ineq_level = first(ineq_level)
  )

ggplot(DATA_irrat_dis, aes(x = reorder(participant, -irrational_not_disapproving), y = irrational_not_disapproving, fill = role)) +
  geom_bar(stat = "identity") +
  labs(x = NULL, y = "Count of irrational not-disapproving") +
  theme(axis.text.x = element_blank(),  
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),  
        panel.background = element_blank()) +  
  ggtitle("Counts of Irrational Not-Disapproving by Participant") +
  scale_fill_manual(values = c("royalblue", "limegreen"))  



```


```{r}
total_count <- DATA_irrat_dis %>%
  group_by(participant) %>%
  summarise(total_irrational = sum(irrational_not_disapproving))

sum(total_count$total_irrational)


percentage_players_0 <- sum(total_count$total_irrational == 0) / n_distinct(total_count$participant) * 100
percentage_players_0_to_3 <- sum(total_count$total_irrational > 0 & total_count$total_irrational <= 3) / n_distinct(total_count$participant) * 100
percentage_players_over_3 <- sum(total_count$total_irrational > 3) / n_distinct(total_count$participant) * 100

share_rich_poor_players_0 <- DATA_irrat_dis %>%
  filter(irrational_not_disapproving == 0) %>%
  group_by(role) %>%
  summarise(count = n()) %>%
  mutate(share = count / sum(count) * 100)

share_rich_poor_players_0_to_3 <- DATA_irrat_dis %>%
  filter(irrational_not_disapproving > 0 & irrational_not_disapproving <= 3) %>%
  group_by(role) %>%
  summarise(count = n()) %>%
  mutate(share = count / sum(count) * 100)

share_rich_poor_players_over_3 <- DATA_irrat_dis %>%
  filter(irrational_not_disapproving > 3) %>%
  group_by(role) %>%
  summarise(count = n()) %>%
  mutate(share = count / sum(count) * 100)

cat("Percentage of players with 0:", percentage_players_0, "%\n")
cat("Percentage of players between 0 and 3:", percentage_players_0_to_3, "%\n")
cat("Percentage of players over 3:", percentage_players_over_3, "%\n\n")

cat("Share of rich and poor players with 0:\n")
print(share_rich_poor_players_0)

cat("\nShare of rich and poor players between 0 and 3:\n")
print(share_rich_poor_players_0_to_3)

cat("\nShare of rich and poor players over 3:\n")
print(share_rich_poor_players_over_3)

share_rich_poor_players_over_9 <- DATA_irrat_dis %>%
  filter(irrational_not_disapproving > 9) %>%
  group_by(role) %>%
  summarise(count = n()) %>%
  mutate(share = count / sum(count) * 100)

print(share_rich_poor_players_over_9)

```

### Per role

```{r}
DATA_am$diff_of_contrib <- DATA_am$activite_A - DATA_am$activite_A_partner
```


```{r}
DATA_am_prop2_poor <- filter(DATA_am_prop2, role == "poor")

count_approbation_2_poor <- sum(DATA_am_prop2_poor$approbation == 0)

percentage <- (count_approbation_2_poor / nrow(DATA_am_prop2_poor)) * 100

print(paste("Percentage of \"poor\" players with prop2 == 1 and approbation == 0: ", percentage, "%"))
```

```{r}
DATA_am_prop2_rich <- filter(DATA_am_prop2, role == "rich")

count_approbation_2_rich <- sum(DATA_am_prop2_rich$approbation == 0)

percentage <- (count_approbation_2_rich / nrow(DATA_am_prop2_rich)) * 100

print(paste("Percentage of \"rich\" players with prop2 == 1 and approbation == 0: ", percentage, "%"))
```

#### Table 2.....................!!!

```{r}
#Accounting for overrepresentation
DATA_am_cont_more <- DATA_am %>% filter(diff_of_contrib > 0)

model1 <- glm(irrational_not_disapproving ~ role + round_number, data = DATA_am_cont_more, family = binomial)

model2 <- glm(irrational_not_disapproving ~ role + diff_of_contrib + round_number, data = DATA_am_cont_more, family = binomial)

model3 <- glm(irrational_not_disapproving ~ role + diff_of_contrib + alpha + role*beta + round_number + understanding_faults, data = DATA_am_cont_more, family = binomial)

vcov1 <- vcovCL(model1, cluster = ~ participant, data = DATA_am_cont_more)
vcov2 <- vcovCL(model2, cluster = ~ participant, data = DATA_am_cont_more)
vcov3 <- vcovCL(model3, cluster = ~ participant, data = DATA_am_cont_more)

coeftest(model1, vcov1)
coeftest(model2, vcov2)
coeftest(model3, vcov3)

cat("Model 1:\n")
cat("Log Likelihood:", logLik(model1), "\n")
cat("Number of Observations:", length(model1$fitted.values), "\n")
cat("AIC:", AIC(model1), "\n\n")

cat("Model 2:\n")
cat("Log Likelihood:", logLik(model2), "\n")
cat("Number of Observations:", length(model2$fitted.values), "\n")
cat("AIC:", AIC(model2), "\n\n")

cat("Model 3:\n")
cat("Log Likelihood:", logLik(model3), "\n")
cat("Number of Observations:", length(model3$fitted.values), "\n")
cat("AIC:", AIC(model3), "\n\n")
```


## Prop 1: Symmetric survive

```{r}
DATA_am$symmetric_contrib <- ifelse(DATA_am$activite_A == DATA_am$activite_A_partner, 1, 0)
nrow(DATA_am)
sum(DATA_am$symmetric_contrib)

sum(DATA_am$symmetric_contrib)/nrow(DATA_am)*100

# Filter the dataset for cases where symmetric_contrib == 1
filtered_data <- DATA_am[DATA_am$symmetric_contrib == 1, ]

# Calculate the total number of cases where approbation == 0 and symmetric_contrib == 1
total_cases <- sum(filtered_data$approbation == 0)

# Calculate the share of these cases where role == "poor"
share_poor <- sum(filtered_data$approbation == 0 & filtered_data$role == "poor") / total_cases * 100

# Calculate the share of these cases where role == "rich"
share_rich <- sum(filtered_data$approbation == 0 & filtered_data$role == "rich") / total_cases * 100

# Print the results
cat("Total cases where approbation == 0 and symmetric_contrib == 1:", total_cases, "\n")
cat("Share of these cases where role == poor:", share_poor, "%\n")
cat("Share of these cases where role == rich:", share_rich, "%\n")

```

# Figures

## Effect of the AM

### Figure 1.......................!!!

```{r}
# Assuming DATA is your original dataset
DATA$trt_role = with(DATA, paste(trt, ineq_level, sep = "_"))

# Aggregate mean contributions by round_number and trt_role
DF = aggregate(final_group_contrib ~ round_number + trt_role, data = DATA, FUN = mean)
colnames(DF) = c("round_number", "trt_role", "mean_contrib")

# Set plot limits
x_range <- range(DF$round_number)
y_range <- range(DF$mean_contrib)

# Plotting
plot(y = DF$mean_contrib[DF$trt_role == "am_low"], x = DF$round_number[DF$trt_role == "am_low"],
     type = "l", col = "firebrick1", lwd = 2,
     xlim = x_range, ylim = y_range,
     main = "Figure 1: Mean Group Contribution Over Time by Treatment and Inequality Level",
     xlab = "Time Period (t)", ylab = "Mean Contribution (G)",
     cex.axis = 1, cex.lab = 1, cex.main = 1, lty ="dashed", bty="L")

points(y = DF$mean_contrib[DF$trt_role == "am_high"], x = DF$round_number[DF$trt_role == "am_high"],
       col = "firebrick1", type = "l", lwd = 2)

points(y = DF$mean_contrib[DF$trt_role == "baseline_low"], x = DF$round_number[DF$trt_role == "baseline_low"],
       col = "orange", type = "l", lwd = 2, lty ="dashed")

points(y = DF$mean_contrib[DF$trt_role == "baseline_high"], x = DF$round_number[DF$trt_role == "baseline_high"],
       col = "orange", type = "l", lwd = 2)

# Add a legend
legend(14, 11, legend = c("MAM and Low", "MAM and High", "Baseline and Low", "Baseline and High"), 
       lty = c("dashed","solid","dashed","solid"), col = c("firebrick1", "firebrick1", "orange", "orange"), bty = "n", cex = 0.8)
```

```{r}
# Wilcoxon test for Low inequality: MAM vs. Baseline
wilcox_test_low <- wilcox.test(
  DATA$g_i[DATA$trt == "am" & DATA$ineq_level == "low"],
  DATA$g_i[DATA$trt == "baseline" & DATA$ineq_level == "low"],
  paired = FALSE # Assuming independent samples
)

# Wilcoxon test for High inequality: MAM vs. Baseline
wilcox_test_high <- wilcox.test(
  DATA$g_i[DATA$trt == "am" & DATA$ineq_level == "high"],
  DATA$g_i[DATA$trt == "baseline" & DATA$ineq_level == "high"],
  paired = FALSE # Assuming independent samples
)

# Printing the results
cat("Wilcoxon test for Low inequality (MAM vs. Baseline):\n")
print(wilcox_test_low)
cat("\nWilcoxon test for High inequality (MAM vs. Baseline):\n")
print(wilcox_test_high)

```
```{r}
# Filter the data for "baseline" treatment
baseline_data <- DATA[DATA$trt == "baseline",]

# Perform the Mann-Kendall trend test for "baseline"
mk_test_baseline <- MannKendall(baseline_data$g_i)

# Print the result for "baseline"
cat("Mann-Kendall trend test for 'baseline':\n")
print(mk_test_baseline)

# Filter the data for "am" treatment
am_data <- DATA[DATA$trt == "am",]

# Perform the Mann-Kendall trend test for "am"
mk_test_am <- MannKendall(am_data$g_i)

# Print the result for "am"
cat("\nMann-Kendall trend test for 'am':\n")
print(mk_test_am)

```

### Figure 2.......................!!!

```{r}
# Assuming DATA is your original dataset
DATA$trt_role = with(DATA, paste(trt, ineq_level, sep = "_"))

# Aggregate mean contributions by round_number and trt_role
DF = aggregate(g_i ~ round_number + trt_role, data = DATA, FUN = mean)
colnames(DF) = c("round_number", "trt_role", "mean_contrib")

# Set plot limits
x_range <- range(DF$round_number)
y_range <- range(DF$mean_contrib)

# Plotting
plot(y = DF$mean_contrib[DF$trt_role == "am_low"], x = DF$round_number[DF$trt_role == "am_low"],
     type = "l", col = "firebrick1", lwd = 2,
     xlim = x_range, ylim = c(2, 11),
     main = "Figure 2: Mean Individual Contribution Over Time by Treatment and Inequality Level",
     xlab = "Time Period", ylab = "Mean Contribution",
     cex.axis = 1, cex.lab = 1, cex.main = 1, lty ="dashed", bty="L")

points(y = DF$mean_contrib[DF$trt_role == "am_high"], x = DF$round_number[DF$trt_role == "am_high"],
       col = "firebrick1", type = "l", lwd = 2)

points(y = DF$mean_contrib[DF$trt_role == "baseline_low"], x = DF$round_number[DF$trt_role == "baseline_low"],
       col = "orange", type = "l", lwd = 2, lty ="dashed")

points(y = DF$mean_contrib[DF$trt_role == "baseline_high"], x = DF$round_number[DF$trt_role == "baseline_high"],
       col = "orange", type = "l", lwd = 2)

# Add a legend
legend(14, 11, legend = c("MAM and Low", "MAM and High", "Baseline and Low", "Baseline and High"), 
       lty = c("dashed","solid","dashed","solid"), col = c("firebrick1", "firebrick1", "orange", "orange"), bty = "n", cex = 0.8)


# Assuming DATA is your original dataset
DATA$trt_role = with(DATA, paste(trt, ineq_level, sep = "_"))

# Aggregate mean contributions by round_number and trt_role
DF = aggregate(activite_A ~ round_number + trt_role, data = DATA, FUN = mean)
colnames(DF) = c("round_number", "trt_role", "mean_prop")

# Set plot limits
x_range <- range(DF$round_number)
y_range <- range(DF$mean_prop)

# Plotting
plot(y = DF$mean_prop[DF$trt_role == "am_low"], x = DF$round_number[DF$trt_role == "am_low"],
     type = "l", col = "firebrick1", lwd = 2,
     xlim = x_range, ylim = c(2, 11),
     main = "Figure 2: Mean Individual Proposition Over Time by Treatment and Inequality Level",
     xlab = "Time Period", ylab = "Mean Proposition",
     cex.axis = 1, cex.lab = 1, cex.main = 1, lty ="dashed", bty="L")

points(y = DF$mean_prop[DF$trt_role == "am_high"], x = DF$round_number[DF$trt_role == "am_high"],
       col = "firebrick1", type = "l", lwd = 2)

points(y = DF$mean_prop[DF$trt_role == "baseline_low"], x = DF$round_number[DF$trt_role == "baseline_low"],
       col = "orange", type = "l", lwd = 2, lty ="dashed")

points(y = DF$mean_prop[DF$trt_role == "baseline_high"], x = DF$round_number[DF$trt_role == "baseline_high"],
       col = "orange", type = "l", lwd = 2)

# Add a legend
legend(14, 7, legend = c("MAM and Low", "MAM and High", "Baseline and Low", "Baseline and High"), 
       lty = c("dashed","solid","dashed","solid"), col = c("firebrick1", "firebrick1", "orange", "orange"), bty = "n", cex = 0.8)

```


```{r}
DATA$trt_binary = ifelse(DATA$trt == "am", 1, 0)
DATA$trt_role = with(DATA, paste(trt_binary, role, sep = "_"))

wilcox.test(g_i ~ ineq_level, data = DATA[DATA$trt_binary == 1, ])
wilcox.test(g_i ~ ineq_level, data = DATA[DATA$trt_binary == 0, ])

wilcox.test(activite_A ~ ineq_level, data = DATA[DATA$trt_binary == 1, ])
wilcox.test(activite_A ~ ineq_level, data = DATA[DATA$trt_binary == 0, ])

wilcox.test(activite_A ~ trt_binary, data = DATA[DATA$ineq_level== "low", ])
wilcox.test(activite_A ~ trt_binary, data = DATA[DATA$ineq_level == "high", ])
```

### Figure 3.......................!!!

```{r}
# Assuming DATA is your original dataset
DATA$trt_binary = ifelse(DATA$trt == "am", 1, 0)
DATA$trt_role = with(DATA, paste(trt_binary, role, sep = "_"))

# Aggregate mean Propositions by round_number and trt_role
DF = aggregate(activite_A ~ round_number + trt_role, data = DATA, FUN = mean)
colnames(DF) = c("round_number", "trt_role", "mean_prop")

# Set plot limits
x_range <- range(DF$round_number)
y_range <- range(DF$mean_prop)

# Plotting
plot(y = DF$mean_prop[DF$trt_role == "1_rich"], x = DF$round_number[DF$trt_role == "1_rich"],
     type = "l", col = "firebrick1", lwd = 2,
     xlim = x_range, ylim = y_range,
     main = "Figure 1: Mean Proposition* Over Time by Treatment and Role",
     xlab = "Time Period", ylab = "Mean Proposition*",
     cex.axis = 1, cex.lab = 1, cex.main = 1, bty="L")

points(y = DF$mean_prop[DF$trt_role == "1_poor"], x = DF$round_number[DF$trt_role == "1_poor"],
       col = "firebrick1", type = "l", lwd = 2, lty = "dashed")

points(y = DF$mean_prop[DF$trt_role == "0_rich"], x = DF$round_number[DF$trt_role == "0_rich"],
       col = "orange", type = "l", lwd = 2)

points(y = DF$mean_prop[DF$trt_role == "0_poor"], x = DF$round_number[DF$trt_role == "0_poor"],
       col = "orange", type = "l", lwd = 2, lty = "dashed")

# Add a legend
legend(15, 7, legend = c("MAM-Rich", "MAM-Poor", "Baseline-Rich", "Baseline-Poor"), 
       lty = c("solid", "dashed", "solid", "dashed"), col = c("firebrick1", "firebrick1", "orange", "orange"), bty = "n", cex = 0.8)

```


```{r}
wilcox.test(activite_A ~ trt_binary, data = DATA[DATA$role == "rich", ])
wilcox.test(activite_A ~ trt_binary, data = DATA[DATA$role == "poor", ])
wilcox.test(activite_A ~ role, data = DATA[DATA$trt_binary == 1, ])
wilcox.test(activite_A ~ role, data = DATA[DATA$trt_binary == 0, ])

DATA$diff_prop_role <- ifelse(DATA$role == "rich", DATA$activite_A - DATA$activite_A_partner, DATA$activite_A_partner - DATA$activite_A)
wilcox.test(diff_prop_role ~ trt_binary, data = DATA)


```

# Main Analysis

## Impact of inequalities on the effectiveness of the AM


```{r}
box_plot <- ggplot(DATA[DATA$trt == "am", ], aes(x = ineq_level, y = final_group_contrib)) +
  geom_boxplot() +
  labs(title = "Distribution of final_group_contrib by ineq_level (trt = am)",
       x = "Inequality Level",
       y = "Final Group Contribution") +
  theme_minimal()
print(box_plot)

am_data <- DATA[DATA$trt == "am", ]
contrib_time_period <- aggregate(final_group_contrib ~ round_number + subtrt, data = am_data, FUN = mean)
print(contrib_time_period)
plot <- ggplot(contrib_time_period, aes(x = round_number, y = final_group_contrib, color = subtrt)) +
  geom_line() +
  labs(title = "Mean Contribution Over Time by Treatment",
       x = "Time Period",
       y = "Mean Contribution") +
  theme_minimal()
print(plot)

kruskal.test(am_data$final_group_contrib ~ am_data$ineq_level)

```


## Effect of AM on inequalities

### Absolute inequality

```{r}
mean_AI_per_subtrt <- DATA %>%
  group_by(subtrt) %>%
  summarise(mean_AI = mean(var_AI, na.rm = TRUE))
print(mean_AI_per_subtrt)

box_plot <- ggplot(DATA, aes(x = subtrt, y = var_AI)) +
  geom_boxplot() +
  labs(title = "Variation of Absolute inequality by Sub treatment",
       x = "Subtrt",
       y = "var AI") +
  theme_minimal()
print(box_plot)

subtrt_values <- c("eq_am", "eq_no_am", "low_am", "low_no_am", "high_am", "high_no_am")
for (value in subtrt_values) {
  subset_data <- DATA %>% filter(subtrt == value)
  
  if (nrow(subset_data) > 1) {
    wilcox_result <- wilcox.test(subset_data$var_AI, mu = 0)
    
    print(paste("Wilcoxon Rank Sum Test for subtrt =", value))
    print(wilcox_result)
  } else {
    print(paste("Insufficient data for subtrt =", value))
  }
}

```

### Relative inequality

```{r}
mean_RI_per_subtrt <- DATA %>%
  group_by(subtrt) %>%
  summarise(mean_RI = mean(var_RI, na.rm = TRUE))
print(mean_RI_per_subtrt)

box_plot <- ggplot(DATA, aes(x = subtrt, y = var_RI)) +
  geom_boxplot() +
  labs(title = "Variation of share of the wealth of the poorest player",
       x = "Subtrt",
       y = "var RI") +
  theme_minimal()
print(box_plot)


subtrt_values <- c("eq_am", "eq_no_am", "low_am", "low_no_am", "high_am", "high_no_am")
for (value in subtrt_values) {
  subset_data <- DATA %>% filter(subtrt == value)
  
  if (nrow(subset_data) > 1) {
    wilcox_result <- wilcox.test(subset_data$var_RI, mu = 0)
    
    print(paste("Wilcoxon Rank Sum Test for subtrt =", value))
    print(wilcox_result)
  } else {
    print(paste("Insufficient data for subtrt =", value))
  }
}

```

## Effect of Inequality aversion

### Append A.4.1...............!!!

```{r}
DATA_ind <- DATA %>%
  group_by(participant) %>%
  summarise(
    mean_g_i = mean(g_i),
    mean_prop = mean(activite_A),
    mean_app = mean(approbation),
    role = first(role),
    beta = mean(beta),
    alpha = first(alpha),
    w_i = first(w_i),
    ineq_level = first(ineq_level),
    trt = first(trt),
    NLE_score = mean(NLE_score),
    gender = first(gender)
  )

DATA_rich <- DATA_ind %>%
  filter(DATA_ind$role == "rich")

reg_model_beta_rich <- lm(mean_prop ~ alpha + beta, data = DATA_rich)
reg_model_beta_rich2 <- lm(mean_prop ~ alpha + beta + ineq_level, data = DATA_rich)
reg_model_beta_rich3 <- lm(mean_prop ~ alpha + beta + ineq_level + trt, data = DATA_rich)
reg_model_beta_rich4 <- lm(mean_prop ~ alpha + beta + ineq_level + trt + gender + NLE_score, data = DATA_rich)

model_list_beta_rich <- list(reg_model_beta_rich, reg_model_beta_rich2, reg_model_beta_rich3, reg_model_beta_rich4)

stargazer(model_list_beta_rich, type = "text",
          star.cutoffs = c(0.05, 0.01, 0.001))

reg_model_beta_rich <- lm(mean_g_i ~ alpha + beta, data = DATA_rich)
reg_model_beta_rich2 <- lm(mean_g_i ~ alpha + beta + ineq_level, data = DATA_rich)
reg_model_beta_rich3 <- lm(mean_g_i ~ alpha + beta + ineq_level + trt, data = DATA_rich)
reg_model_beta_rich4 <- lm(mean_g_i ~ alpha + beta + ineq_level + trt + gender + NLE_score, data = DATA_rich)

model_list_beta_rich <- list(reg_model_beta_rich, reg_model_beta_rich2, reg_model_beta_rich3, reg_model_beta_rich4)

stargazer(model_list_beta_rich, type = "text",
          star.cutoffs = c(0.05, 0.01, 0.001))




```

### Append A.4.2...............!!!


```{r}

# Create dummies
DATA_ind2 <- DATA_ind %>%
  mutate(
    dummy1 = ifelse(beta < 1, 1, 0),
    dummy2 = ifelse(beta <= alpha, 1, 0)
  )

# Filter dataset for participants where both dummies are 1
filtered_DATA_ind <- DATA_ind2 %>%
  filter(dummy1 == 1 & dummy2 == 1)

DATA_rich <- filtered_DATA_ind %>%
  filter(filtered_DATA_ind$role == "rich")

reg_model_beta_rich <- lm(mean_prop ~ alpha + beta, data = DATA_rich)
reg_model_beta_rich2 <- lm(mean_prop ~ alpha + beta + ineq_level, data = DATA_rich)
reg_model_beta_rich3 <- lm(mean_prop ~ alpha + beta + ineq_level + trt, data = DATA_rich)
reg_model_beta_rich4 <- lm(mean_prop ~ alpha + beta + ineq_level + trt + gender + NLE_score, data = DATA_rich)
vif(reg_model_beta_rich4)

model_list_beta_rich <- list(reg_model_beta_rich, reg_model_beta_rich2, reg_model_beta_rich3, reg_model_beta_rich4)

stargazer(model_list_beta_rich, type = "text",
          star.cutoffs = c(0.05, 0.01, 0.001))

reg_model_beta_rich <- lm(mean_g_i ~ alpha + beta, data = DATA_rich)
reg_model_beta_rich2 <- lm(mean_g_i ~ alpha + beta + ineq_level, data = DATA_rich)
reg_model_beta_rich3 <- lm(mean_g_i ~ alpha + beta + ineq_level + trt, data = DATA_rich)
reg_model_beta_rich4 <- lm(mean_g_i ~ alpha + beta + ineq_level + trt + gender + NLE_score, data = DATA_rich)

model_list_beta_rich <- list(reg_model_beta_rich, reg_model_beta_rich2, reg_model_beta_rich3, reg_model_beta_rich4)


stargazer(model_list_beta_rich, type = "text",
          star.cutoffs = c(0.05, 0.01, 0.001))

```

### Append A.5.1...............!!!

```{r}
DATA_poor <- DATA %>%
  filter(DATA$role == "poor")

DATA_poor <- DATA_poor %>%
  group_by(participant) %>%
  summarise(
    mean_g_i = mean(g_i),
    mean_prop = mean(activite_A),
    beta = mean(beta),
    alpha = first(alpha),
    ineq_level = first(ineq_level),
    trt = first(trt),
    gender = first(gender),
    NLE_score = first(NLE_score)
  )

reg_model_alpha_poor3 <- lm(mean_prop ~ alpha + beta + ineq_level + trt, data = DATA_poor)
reg_model_alpha_poor4 <- lm(mean_prop ~ alpha + beta + ineq_level + trt + gender + NLE_score, data = DATA_poor)

model_list_alpha_poor <- list(reg_model_alpha_poor3, reg_model_alpha_poor4)

stargazer(model_list_alpha_poor, type = "text",
          star.cutoffs = c(0.05, 0.01, 0.001))

reg_model_alpha_poor3 <- lm(mean_g_i ~ alpha + beta + ineq_level + trt, data = DATA_poor)
reg_model_alpha_poor4 <- lm(mean_g_i ~ alpha + beta + ineq_level + trt + gender + NLE_score, data = DATA_poor)

model_list_alpha_poor <- list(reg_model_alpha_poor3, reg_model_alpha_poor4)

stargazer(model_list_alpha_poor, type = "text",
          star.cutoffs = c(0.05, 0.01, 0.001))

```

### Append A.5.2...............!!!

```{r}
DATA_poor <- DATA_poor %>%
  mutate(
    dummy1 = ifelse(beta < 1, 1, 0),
    dummy2 = ifelse(beta <= alpha, 1, 0)
  )

filtered_DATA_poor <- DATA_poor %>%
  filter(dummy1 == 1 & dummy2 == 1)

reg_model_alpha_poor3 <- lm(mean_prop ~ alpha + beta + ineq_level + trt, data = filtered_DATA_poor)
reg_model_alpha_poor4 <- lm(mean_prop ~ alpha + beta + ineq_level + trt + gender + NLE_score, data = filtered_DATA_poor)

model_list_alpha_poor <- list(reg_model_alpha_poor3, reg_model_alpha_poor4)

stargazer(model_list_alpha_poor, type = "text",
          star.cutoffs = c(0.05, 0.01, 0.001))

reg_model_alpha_poor3 <- lm(mean_g_i ~ alpha + beta + ineq_level + trt, data = DATA_poor)
reg_model_alpha_poor4 <- lm(mean_g_i ~ alpha + beta + ineq_level + trt + gender + NLE_score, data = DATA_poor)

model_list_alpha_poor <- list(reg_model_alpha_poor3, reg_model_alpha_poor4)

stargazer(model_list_alpha_poor, type = "text",
          star.cutoffs = c(0.05, 0.01, 0.001))
```

# Exploratory analysis

## Table 3...........................!!!

```{r}
rich_players <- DATA[DATA$role == "rich",]
rich_players <- rich_players[rich_players$trt == "baseline",]

wilcox_test_overall <- wilcox.test(rich_players$activite_A, rich_players$belief_A_other, paired = TRUE)
cat("Overall Wilcoxon signed-rank test between activite_A and belief_A_other for rich players:\n")
print(wilcox_test_overall)

rich_high <- rich_players[rich_players$role == "rich" & rich_players$ineq_level == "high",]

wilcox_test_high <- wilcox.test(rich_high$activite_A, rich_high$belief_A_other, paired = TRUE)
cat("High Inequality Level Wilcoxon signed-rank test between activite_A and belief_A_other for rich players:\n")
print(wilcox_test_high)

rich_low <- rich_players[rich_players$role == "rich" & rich_players$ineq_level == "low",]

wilcox_test_low <- wilcox.test(rich_low$activite_A, rich_low$belief_A_other, paired = TRUE)
cat("Low Inequality Level Wilcoxon signed-rank test between activite_A and belief_A_other for rich players:\n")
print(wilcox_test_low)


calculate_means_sds <- function(rich_players_subset) {
  mean_activite_A <- mean(rich_players_subset$activite_A, na.rm = TRUE)
  sd_activite_A <- sd(rich_players_subset$activite_A, na.rm = TRUE)
  mean_belief_A_other <- mean(rich_players_subset$belief_A_other, na.rm = TRUE)
  sd_belief_A_other <- sd(rich_players_subset$belief_A_other, na.rm = TRUE)
  
  c(mean_activite_A, sd_activite_A, mean_belief_A_other, sd_belief_A_other)
}

overall_stats <- calculate_means_sds(rich_players)
high_stats <- calculate_means_sds(rich_high)
low_stats <- calculate_means_sds(rich_low)

table_content <- rbind(
  c("Overall", 
    paste(round(overall_stats[1], 2), "(", round(overall_stats[2], 2), ")", sep=""),
    paste(round(overall_stats[3], 2), "(", round(overall_stats[4], 2), ")", sep=""),
    formatC(wilcox_test_overall$p.value, format = "e", digits = 2)),
  c("High Inequality Level", 
    paste(round(high_stats[1], 2), "(", round(high_stats[2], 2), ")", sep=""),
    paste(round(high_stats[3], 2), "(", round(high_stats[4], 2), ")", sep=""),
    formatC(wilcox_test_high$p.value, format = "e", digits = 2)),
  c("Low Inequality Level", 
    paste(round(low_stats[1], 2), "(", round(low_stats[2], 2), ")", sep=""),
    paste(round(low_stats[3], 2), "(", round(low_stats[4], 2), ")", sep=""),
    formatC(wilcox_test_low$p.value, format = "e", digits = 2))
)

table_df <- as.data.frame(table_content, stringsAsFactors = FALSE)
colnames(table_df) <- c("Group Comparison", "Mean Activite_A (SD)", "Mean Belief_A_Other (SD)", "Wilcoxon Test p-value")

table_df$Significance <- ifelse(as.numeric(table_df$`Wilcoxon Test p-value`) < 0.001, "***",
                                ifelse(as.numeric(table_df$`Wilcoxon Test p-value`) < 0.01, "**",
                                       ifelse(as.numeric(table_df$`Wilcoxon Test p-value`) < 0.05, "*", "")))

table_df <- table_df[, c("Group Comparison", "Mean Activite_A (SD)", "Mean Belief_A_Other (SD)", "Wilcoxon Test p-value", "Significance")]

print(table_df)

```

```{r}
poor_players <- DATA[DATA$role == "poor",]
poor_players <- poor_players[poor_players$trt == "baseline",]

wilcox_test_overall <- wilcox.test(poor_players$activite_A, poor_players$belief_A_other, paired = TRUE)
cat("Overall Wilcoxon signed-rank test between activite_A and belief_A_other for poor players:\n")
print(wilcox_test_overall)

poor_high <- poor_players[poor_players$role == "poor" & poor_players$ineq_level == "high",]

wilcox_test_high <- wilcox.test(poor_high$activite_A, poor_high$belief_A_other, paired = TRUE)
cat("High Inequality Level Wilcoxon signed-rank test between activite_A and belief_A_other for poor players:\n")
print(wilcox_test_high)

poor_low <- poor_players[poor_players$role == "poor" & poor_players$ineq_level == "low",]

wilcox_test_low <- wilcox.test(poor_low$activite_A, poor_low$belief_A_other, paired = TRUE)
cat("Low Inequality Level Wilcoxon signed-rank test between activite_A and belief_A_other for poor players:\n")
print(wilcox_test_low)

calculate_means_sds <- function(poor_players_subset) {
  mean_activite_A <- mean(poor_players_subset$activite_A, na.rm = TRUE)
  sd_activite_A <- sd(poor_players_subset$activite_A, na.rm = TRUE)
  mean_belief_A_other <- mean(poor_players_subset$belief_A_other, na.rm = TRUE)
  sd_belief_A_other <- sd(poor_players_subset$belief_A_other, na.rm = TRUE)
  
  c(mean_activite_A, sd_activite_A, mean_belief_A_other, sd_belief_A_other)
}

overall_stats <- calculate_means_sds(poor_players)
high_stats <- calculate_means_sds(poor_high)
low_stats <- calculate_means_sds(poor_low)

table_content <- rbind(
  c("Overall", 
    paste(round(overall_stats[1], 2), "(", round(overall_stats[2], 2), ")", sep=""),
    paste(round(overall_stats[3], 2), "(", round(overall_stats[4], 2), ")", sep=""),
    formatC(wilcox_test_overall$p.value, format = "e", digits = 2)),
  c("High Inequality Level", 
    paste(round(high_stats[1], 2), "(", round(high_stats[2], 2), ")", sep=""),
    paste(round(high_stats[3], 2), "(", round(high_stats[4], 2), ")", sep=""),
    formatC(wilcox_test_high$p.value, format = "e", digits = 2)),
  c("Low Inequality Level", 
    paste(round(low_stats[1], 2), "(", round(low_stats[2], 2), ")", sep=""),
    paste(round(low_stats[3], 2), "(", round(low_stats[4], 2), ")", sep=""),
    formatC(wilcox_test_low$p.value, format = "e", digits = 2))
)

table_df <- as.data.frame(table_content, stringsAsFactors = FALSE)
colnames(table_df) <- c("Group Comparison", "Mean Activite_A (SD)", "Mean Belief_A_Other (SD)", "Wilcoxon Test p-value")

table_df$Significance <- ifelse(as.numeric(table_df$`Wilcoxon Test p-value`) < 0.001, "***",
                                ifelse(as.numeric(table_df$`Wilcoxon Test p-value`) < 0.01, "**",
                                       ifelse(as.numeric(table_df$`Wilcoxon Test p-value`) < 0.05, "*", "")))

table_df <- table_df[, c("Group Comparison", "Mean Activite_A (SD)", "Mean Belief_A_Other (SD)", "Wilcoxon Test p-value", "Significance")]

print(table_df)

```

```{r}
rich_players <- DATA[DATA$role == "rich",]
rich_players <- rich_players[rich_players$trt == "am",]

wilcox_test_overall <- wilcox.test(rich_players$activite_A, rich_players$belief_A_other, paired = TRUE)
cat("Overall Wilcoxon signed-rank test between activite_A and belief_A_other for rich players:\n")
print(wilcox_test_overall)

rich_high <- rich_players[rich_players$role == "rich" & rich_players$ineq_level == "high",]

wilcox_test_high <- wilcox.test(rich_high$activite_A, rich_high$belief_A_other, paired = TRUE)
cat("High Inequality Level Wilcoxon signed-rank test between activite_A and belief_A_other for rich players:\n")
print(wilcox_test_high)

rich_low <- rich_players[rich_players$role == "rich" & rich_players$ineq_level == "low",]

wilcox_test_low <- wilcox.test(rich_low$activite_A, rich_low$belief_A_other, paired = TRUE)
cat("Low Inequality Level Wilcoxon signed-rank test between activite_A and belief_A_other for rich players:\n")
print(wilcox_test_low)

calculate_means_sds <- function(rich_players_subset) {
  mean_activite_A <- mean(rich_players_subset$activite_A, na.rm = TRUE)
  sd_activite_A <- sd(rich_players_subset$activite_A, na.rm = TRUE)
  mean_belief_A_other <- mean(rich_players_subset$belief_A_other, na.rm = TRUE)
  sd_belief_A_other <- sd(rich_players_subset$belief_A_other, na.rm = TRUE)
  
  c(mean_activite_A, sd_activite_A, mean_belief_A_other, sd_belief_A_other)
}

overall_stats <- calculate_means_sds(rich_players)
high_stats <- calculate_means_sds(rich_high)
low_stats <- calculate_means_sds(rich_low)

table_content <- rbind(
  c("Overall", 
    paste(round(overall_stats[1], 2), "(", round(overall_stats[2], 2), ")", sep=""),
    paste(round(overall_stats[3], 2), "(", round(overall_stats[4], 2), ")", sep=""),
    formatC(wilcox_test_overall$p.value, format = "e", digits = 2)),
  c("High Inequality Level", 
    paste(round(high_stats[1], 2), "(", round(high_stats[2], 2), ")", sep=""),
    paste(round(high_stats[3], 2), "(", round(high_stats[4], 2), ")", sep=""),
    formatC(wilcox_test_high$p.value, format = "e", digits = 2)),
  c("Low Inequality Level", 
    paste(round(low_stats[1], 2), "(", round(low_stats[2], 2), ")", sep=""),
    paste(round(low_stats[3], 2), "(", round(low_stats[4], 2), ")", sep=""),
    formatC(wilcox_test_low$p.value, format = "e", digits = 2))
)

table_df <- as.data.frame(table_content, stringsAsFactors = FALSE)
colnames(table_df) <- c("Group Comparison", "Mean Activite_A (SD)", "Mean Belief_A_Other (SD)", "Wilcoxon Test p-value")

table_df$Significance <- ifelse(as.numeric(table_df$`Wilcoxon Test p-value`) < 0.001, "***",
                                ifelse(as.numeric(table_df$`Wilcoxon Test p-value`) < 0.01, "**",
                                       ifelse(as.numeric(table_df$`Wilcoxon Test p-value`) < 0.05, "*", "")))

table_df <- table_df[, c("Group Comparison", "Mean Activite_A (SD)", "Mean Belief_A_Other (SD)", "Wilcoxon Test p-value", "Significance")]

print(table_df)

```

```{r}
poor_players <- DATA[DATA$role == "poor",]
poor_players <- poor_players[poor_players$trt == "am",]

wilcox_test_overall <- wilcox.test(poor_players$activite_A, poor_players$belief_A_other, paired = TRUE)
cat("Overall Wilcoxon signed-rank test between activite_A and belief_A_other for poor players:\n")
print(wilcox_test_overall)

poor_high <- poor_players[poor_players$role == "poor" & poor_players$ineq_level == "high",]

wilcox_test_high <- wilcox.test(poor_high$activite_A, poor_high$belief_A_other, paired = TRUE)
cat("High Inequality Level Wilcoxon signed-rank test between activite_A and belief_A_other for poor players:\n")
print(wilcox_test_high)

poor_low <- poor_players[poor_players$role == "poor" & poor_players$ineq_level == "low",]

wilcox_test_low <- wilcox.test(poor_low$activite_A, poor_low$belief_A_other, paired = TRUE)
cat("Low Inequality Level Wilcoxon signed-rank test between activite_A and belief_A_other for poor players:\n")
print(wilcox_test_low)

calculate_means_sds <- function(poor_players_subset) {
  mean_activite_A <- mean(poor_players_subset$activite_A, na.rm = TRUE)
  sd_activite_A <- sd(poor_players_subset$activite_A, na.rm = TRUE)
  mean_belief_A_other <- mean(poor_players_subset$belief_A_other, na.rm = TRUE)
  sd_belief_A_other <- sd(poor_players_subset$belief_A_other, na.rm = TRUE)
  
  c(mean_activite_A, sd_activite_A, mean_belief_A_other, sd_belief_A_other)
}

overall_stats <- calculate_means_sds(poor_players)
high_stats <- calculate_means_sds(poor_high)
low_stats <- calculate_means_sds(poor_low)

table_content <- rbind(
  c("Overall", 
    paste(round(overall_stats[1], 2), "(", round(overall_stats[2], 2), ")", sep=""),
    paste(round(overall_stats[3], 2), "(", round(overall_stats[4], 2), ")", sep=""),
    formatC(wilcox_test_overall$p.value, format = "e", digits = 2)),
  c("High Inequality Level", 
    paste(round(high_stats[1], 2), "(", round(high_stats[2], 2), ")", sep=""),
    paste(round(high_stats[3], 2), "(", round(high_stats[4], 2), ")", sep=""),
    formatC(wilcox_test_high$p.value, format = "e", digits = 2)),
  c("Low Inequality Level", 
    paste(round(low_stats[1], 2), "(", round(low_stats[2], 2), ")", sep=""),
    paste(round(low_stats[3], 2), "(", round(low_stats[4], 2), ")", sep=""),
    formatC(wilcox_test_low$p.value, format = "e", digits = 2))
)

table_df <- as.data.frame(table_content, stringsAsFactors = FALSE)
colnames(table_df) <- c("Group Comparison", "Mean Activite_A (SD)", "Mean Belief_A_Other (SD)", "Wilcoxon Test p-value")

table_df$Significance <- ifelse(as.numeric(table_df$`Wilcoxon Test p-value`) < 0.001, "***",
                                ifelse(as.numeric(table_df$`Wilcoxon Test p-value`) < 0.01, "**",
                                       ifelse(as.numeric(table_df$`Wilcoxon Test p-value`) < 0.05, "*", "")))

table_df <- table_df[, c("Group Comparison", "Mean Activite_A (SD)", "Mean Belief_A_Other (SD)", "Wilcoxon Test p-value", "Significance")]

print(table_df)

```